Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/related.tex
Jed added a few citations and put a note in the the related works for them
Jed added a paragraph at the end of related.tex

>>>>

Routing and its interplay with Internet censorship, surveillance, and related
issues is a general research area with a broad set of research questions.
Karlin \emph{et al.}~\cite{DBLP:journals/corr/abs-0903-3218} considered the
centrality of countries with respect to routing of other nations' traffic, a
related problem that is distinct from chokepoints to monitor/control traffic
into and out of a government's own country.  Dainotti \emph{et
al.}~\cite{Dainotti:2011:ACI:2068816.2068818} anlyze two specific large-scale
Internet disruptions at the routing level.  Khattak \emph{et
al.}~\cite{Khattak:2014:LCI:2663716.2663750} performed a detailed analysis of
censorship at the ISP level in Pakistan.
